### 2019-09-12 2019_neurips_vigil/experiments.tex

The first approach is to train a model on the hard train set only and test it on the test set. It is the same approach used by the original COG paper ~\cite{cog2018} to evaluate performance on the hard data set. We achieve a test accuracy of … which represents a major improvement from the COG model score.

@@

Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard data set. Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represent the state of the art accuracy for the hard setting (classification tasks).
After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy from the first approach.

>>>>

The first approach is to train a model on the hard train set only and test it on the hard test set. It is the same approach used by the original COG paper ~\cite{cog2018} to evaluate performance on the hard data set. We achieve a test accuracy of … which represents a major improvement from the COG model score.

@@

Finally we train a model on the canonical data set, fine-tune it on the hard data set during only 25k iterations and test it on the hard data set. Thanks to fine-tuning, we can observe a significant improvement from 91.6\%  to 96.5\% test accuracy which represent the state of the art accuracy for the hard setting (classification tasks).
After a short fine-tuning process, the model can generalize well to harder tasks and even surpass the accuracy obtained in the first approach.
